Digitization of the Australian Parliamentary Debates (1901-2022)

### 2022-10-17 paper/paper.qmd
fixed graphs

@@

@@

# plot of total number of sitting days per year
all_files %>% 
  filter(year!=2022) %>% 
  group_by(year) %>% 
  summarise(tot_days = sum(unique(day))) %>% 
  ggplot(aes(x=year, y=tot_days)) + 
  geom_point() +
  geom_line() + 
  theme_bw() +
  labs(x = "Year", 
       y = "Count", 
       title = "Total number of sitting days per year (2000-2021)")

@@

all_files %>% 
  filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
  mutate(month_abb = month.abb[month]) %>% 
  group_by(year, month_abb) %>% 
  summarise(avg_days = mean(unique(day))) %>% 
  ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
  geom_col() + 
  facet_wrap(~year) +
  theme_bw() + 
  labs(x = "Month", 
       y="Average sitting days", 
       title = "Average number of sitting days per month (2015-2020)") +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
```

@@

The approach to parsing contents of an XML document is heavily dependent on its tree structure. As such, to create this database, we started by looking at a single Hansard transcript in XML form. Doing so enabled us to understand the various components of interest in the document, and how each one can be parsed according to its corresponding structural form. For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them. Extracting and correctly organizing these nested sub-elements required careful consideration. ---- this sentence feels incomplete / out of place -------. Parsing was performed in `R` using the `XML` package. Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible. Further, since we are looking at such a wide time span of these documents, there are expectedly a number of changes in the way they are formatted. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting. As mentioned in section @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.

@@

The XML structure begins with a root or parent element "hansard", followed by a child element "session header" with sub-child elements with information such as the date, and parliament number. Next there is a child element containing everything that takes place in the Chamber, "chamber.xscript". On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too. This allows for the distinction of proceedings of the Chamber and Federation Chamber. Each proceeding begins with a business start, naming the speaker and what time they took the chair. Next comes the debates and nested sub-debates. Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it. That said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of these three elements as well as their respective sub-elements contain important information on the title of the debate or sub-debate, who is speaking, and what is being said. As mentioned, in many cases speeches are interrupted by interjections, which are embedded in these sub-elements as well. The final key distinct component of Hansard is Question Time, in which question and answer elements are classified differently than general debate text. Sometimes questions and answers are nested within debate or sub-debate child nodes, and other times they have their own child node. More detail on the processing of Question Time will follow in @sec-qa.

>>>>

cases where unsure how to proceed w xml always deferred to pdf

@@

to this point various researchers have had to create

- tim sherrett (historic hansard) - 
- patrick leslie has also created a dataset as have others
rework paragrpah about how these have been used

no comprehensive dataset based on xml that goes from 1901-today
1930s and before - ocr ruins accuracy (earlier decades)

@@

# plot of total number of sitting days per year
# numbers are wrong
all_files %>% 
  filter(year!=2022) %>% 
  group_by(year) %>% 
  summarise(tot_days = n()) %>% 
  ggplot(aes(x=year, y=tot_days)) + 
  geom_point() +
  geom_line() + 
  theme_bw() +
  labs(x = "Year", 
       y = "Count", 
       title = "Total number of sitting days per year (2000-2021)")

@@

all_files %>% 
  filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
  mutate(month_abb = month.abb[month]) %>% 
  group_by(year, month_abb) %>% 
  summarise(avg_days = n()) %>% 
  ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
  geom_col() + 
  facet_wrap(~year) +
  theme_bw() + 
  labs(x = "Month", 
       y="Count", 
       title = "Number of sitting days per month (2015-2020)") +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
```

@@

The approach to parsing contents of an XML document is heavily dependent on its tree structure. As such, to create this database, we started by looking at a single Hansard transcript in XML form. Doing so enabled us to understand the various components of interest in the document, and how each one can be parsed according to its corresponding structural form. For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them. Parsing was performed in `R` using the `XML` package. Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible. Further, since we are looking at such a wide time span of documents, there are expectedly a number of changes in the way they are formatted. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting. As mentioned in @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.

@@

The XML structure begins with a root or parent element `"hansard"`, followed by a child element `"session.header"` with sub-child elements with information such as the date, and parliament number. Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`. On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too. This allows for the distinction of proceedings of the Chamber and Federation Chamber. Each proceeding begins with a business start, naming the speaker and what time they took the chair. Next comes the debates and nested sub-debates. Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it. That said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of these three elements as well as their respective sub-elements contain important information on the title of the debate or sub-debate, who is speaking, and what is being said. As mentioned, in many cases speeches are interrupted by interjections, which are embedded in these sub-elements as well. The final key distinct component of Hansard is Question Time, in which question and answer elements are classified differently than general debate text. Sometimes questions and answers are nested within debate or sub-debate child nodes, and other times they have their own child node. More detail on the processing of Question Time will follow in @sec-qa.
